### 2019-05-08 paper/plots/mc/plot.tex
added river swim experiment

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=6cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Average Return}]

>>>>

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Return}]

### 2019-05-08 paper/plots/riverswim/plot_main.tex
added river swim experiment

\documentclass{standalone} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}

@@

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 2 by 2},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
%        		\nextgroupplot[title={}, 
%        					   xlabel={Episodes},
%        					   ylabel={Cumulative Average Return}]
%        			
%        			\drawplot{OPTIMIST discrete 20}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdisc}{4}
%        			\drawplot{OPTIMIST discrete 100}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdiscc}{4}
%        			\drawplot{OPTIMIST2 ($k=2$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontd}{4}
%        			\drawplot{OPTIMIST2 ($k=3$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontt}{4}
%        			\drawplot{OPTIMIST2 ($k=4$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontq}{4}
%        			\drawplot{PGPE}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\pgpe}{1}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

        			\drawplot{OPTIMIST discrete 20}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontq}{4}
        			\drawplot{PGPE}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\pgpe}{1}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Per-Step Regret}]

        			\drawplot{OPTIMIST discrete 20}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontq}{4}
        			\drawplot{PGPE}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\pgpe}{1}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Probability Right action}]

        			\drawplot{OPTIMIST discrete 20}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontq}{4}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Grid Size}]

        			\drawplot{OPTIMIST discrete 20}{GridSize_mean}{GridSize_up}{GridSize_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{GridSize_mean}{GridSize_up}{GridSize_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontq}{4}

@@

			\path (myplot c1r1.south west|-current bounding box.south)--
      			coordinate(legendpos)
      			(myplot c2r1.south east|-current bounding box.south);
			\matrix[matrix of nodes,
    				anchor=north,
    				inner sep=0.4em,
    				draw=none,
    				font=\rmfamily%\scriptsize\rmfamily
  					]at([yshift=0ex]legendpos)
  					{ 	
						\ref{plots:OPTIMIST discrete 20}& OPTIMIST (20 arms)&
    					\ref{plots:OPTIMIST discrete 100}& OPTIMIST (100 arms)&
    					\ref{plots:OPTIMIST2 ($k=2$)}& OPTIMIST2 ($\kappa=2$)\\
    					\ref{plots:OPTIMIST2 ($k=3$)}& OPTIMIST2 ($\kappa=3$)&	
    					\ref{plots:OPTIMIST2 ($k=4$)}& OPTIMIST2 ($\kappa=4$)&	
    					\ref{plots:PGPE}& PGPE\\	
    					};

>>>>

\documentclass{standalone} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}

@@

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  xtick={0,1000,2000,3000,4000,5000},
							  legend style={thin, draw=gray, at={(0.95,0.32)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Return}]

        			\drawplot{OPTIMIST discrete 20}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdisc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontd}{4}
        			\drawplot{}{}{}{}{}{}
        			\drawplot{PGPE}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\pgpe}{1}
        			\legend{OPTIMIST (20 arms),OPTIMIST2 ($\kappa=2$),,PGPE};

@@
